Hybrid platforms and bargaining

### 2023-06-11 src/presentation/io_day.qmd
Reorganize slides

::: {.incremental}
 - Free entry equilibrium: fringe firms make zero net profits
   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
 - In order to guarantee uniqueness, let us assume
   $$
   \scriptsize
   \begin{gather*}
       f'_{n_F} (N_P, N_F) < \int_0^1 s f'_{n_F} (N_P, s N_F) \mathrm{d}s \\
       \text{or} \\
       f''_{n_F} (N_P, N_F) < \int_0^1 s^2 f''_{n_F} (N_P, s N_F) \mathrm{d}s.
   \end{gather*}
   $$
     - Holds for certain interesting cases, such as the example application
:::

@@

@@

@@

>>>>

::: {.incremental}
 - Free entry equilibrium: fringe firms make zero net profits
   $$ \pi_F(N_P, N_F^*) = I_F N_F^* $$
 - An extra assumption on $f$ is needed for uniqueness.
   - It guarantees a concave or hump-shaped $\pi_F(N_P, N_F^*)$
   - It is satisfied in the example application
:::

@@

::: {.crossref .fragment}
Microfoundations: @sec-utility-function
:::

@@

<!-- TODO: CS instead of A, labels -->

@@

## Utility function {#sec-utility-function}
